Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-22 WSSSPE3/report/WSSSPE3_review.tex
small wording fix

WSSSPE3 broke free of the traditional Supercomputing Conference environment this
year, and in Turk's words, it spoke to the fact that scientific software comes
from many different types of inquiries, deployment, strategies for maintenance,
users; and ways of measuring the value of a piece of software. It appeared to
Turk that the supercomputing conferences generally adopt some top-down
approaches, whereas SciPy more often than not uses more bottom-up systems. The essential
messages perceived were also often polar: software getting harder in
supercomputing communities with exascale computing and optimization issues in
mind, but software becoming better in the SciPy group with emerging tools such
as Jupiter and productivity packages for research workflow. Admitting such
comparisons are somewhat unfair generalizations, Turk reminded the audience that
the different approaches bring different types of ideas to the table, but he
welcomed WSSSPE3 being conducted outside existing preconceptions.

>>>>

WSSSPE3 broke free of the traditional Supercomputing Conference environment this
year, and in Turk's words, it spoke to the fact that scientific software comes
from many different types of inquiries, deployment, strategies for maintenance,
users; and ways of measuring the value of a piece of software. It appeared to
Turk that the supercomputing conferences generally adopt some top-down
approaches, whereas SciPy more often than not uses more bottom-up systems. The essential
messages perceived were also often bipolar: software getting harder in
supercomputing communities with exascale computing and optimization issues in
mind, but software becoming better in the SciPy group with emerging tools such
as Jupiter and productivity packages for research workflow. Admitting such
comparisons are somewhat unfair generalizations, Turk reminded the audience that
the different approaches bring different types of ideas to the table, but he
welcomed WSSSPE3 being conducted outside existing preconceptions.
